### 2020-02-06 README.Rmd
found the problem for why the SCBI and BW histograms looked different

```{r}
census_df1 <- bw_2008
census_df2 <- bw_2014
id <- "treeID"

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id)
```

@@

```{r, cache = TRUE}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.5) +
  labs(x = "Average annual growth in dbh") +
  coord_cartesian(xlim = c(-5, 10))
```

>>>>

```{r}
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% filter(codes != 'R')
id <- "treeID"

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10)
```

@@

```{r, cache = TRUE}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh") +
  coord_cartesian(xlim = c(-0.5, 1))
```
